Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-19 draft.tex
some proofreading, potential operators, mixed bc pf inequality

>>>>

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $\Gamma = F_{1} \cup \dots \cup F_{\ell}$ be the union of $\ell+1$ different faces of $T$. 
    Suppose that $u \in W^{2}\Lambda^{k}(T)$ such that 
    $\trace_{T,\Gamma} u = 0$.
    Then there exists $w \in W^{2}\Lambda^{k}(T)$ such that 
    $\trace_{T,\Gamma} w = 0$
    and  
    \begin{align*}
        \cartan w = \cartan u,
        \quad 
        \| w \|_{L^{2}(\Omega)} 
        \leq 
        C_{\PF,\Gamma,\ell,k,2}(T)
        \| \cartan u \|_{L^{2}(\Omega)}
        .
    \end{align*}
    Here, $C_{\PF,\Gamma,\ell,k,2}(T) > 0$ is a constant such that 
    \begin{align*}
        C_{\PF,\Gamma,\ell,k,2}(T)
        \leq 
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    If $\ell = n$, then the Poincar\'e--Friedrichs constant is obtained via duality from the case without boundary conditions, 
    so we only consider the case $\ell < n$.
    There exists an affine bijection $\varphi : \Delta^n \rightarrow T$ 
    that maps 
    the face of $\Delta^n$
    orthogonal to the $i$-th coordinate axis, written $\hat F_{i} \subseteq \Delta^n$ here, is mapped onto the face $F_{i-1}$ for $1 \leq i \leq \ell+1$.
    We write $\hat \Gamma := \hat F_{1} \cup \dots \cup \hat F_{\ell+1}$.
    Note that $\hat\Gamma$ does not include the face of the reference simplex whose vertices are the $n$ canonical unit vectors.

    Let $\hat u \in W^{2}\Lambda^{k}(\hat T)$ such that $\trace_{\hat T,\hat\Gamma} u = 0$.
    By exactness of the de~Rham complex over the reference with simplex 
    with tangential boundary conditions along $\hat\Gamma$, which is a topological ball, 
    we conclude that there exists $w \in W^{2}\Lambda^{k}(T)$ satisfying the conditions $\trace_{T,\Gamma} w = 0$
    and $\cartan w = \cartan u$ and such that $w$ has minimal norm among the members of $W^{2}\Lambda^{k}(T)$ satisfying these two conditions.
    Under these conditions, we have the Gaffney inequality 
    \begin{align}\color{red}
        \| \nabla \hat w \|_{L^{2}(\Delta^{n})}
        \leq 
        C_{??}
        \| \cartan \hat w \|_{L^{2}(\Delta^{n})}
        .
    \end{align}
    We write $w$ as in \eqref{math:canonicalrepresentation},
    \begin{gather}
        w
        = 
        \sum_{ \sigma \in \Sigma(k,n) } 
        w_{\sigma} \, 
        \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
    \end{gather}
    If $\sigma \in \Sigma(k,n)$ and its range does not contain some $1 \leq i \leq \ell+1$,
    then the boundary conditions imply that $\trace_{T,F_{i}} w_{\sigma} = 0$.
    Then Friedrichs inequality with partial boundary conditions, Lemma~\ref{lemma:mixedbconsimplex},
    implies 
    \begin{align*}
        \| w_{\sigma} \|_{L^{2}(T)}
        &
        \leq 
        \frac{\diam(T)}{\sqrt{2}}
        \| \nabla w \|_{L^{2}(T)}
        .
    \end{align*}
    We then define $w'_{\sigma} := w_{\sigma}$.

    If $\sigma \in \Sigma(k,n)$ and its range does not contain any $1 \leq i \leq \ell+1$,
    then no boundary conditions are imposed on that component but the classical Poincar\'e--Friedrichs inequality implies 
    \begin{align*}
        \| w_{\sigma} - w_{\sigma,\Omega} \|_{L^{2}(T)}
        &
        \leq 
        \frac{\diam(T)}{\pi}
        \| \nabla w \|_{L^{2}(T)}
        .
    \end{align*}
    We then define $w'_{\sigma} = w_{\sigma} - w_{\sigma,\Omega}$.

    This defines a new differential form 
    \begin{gather}
        w'
        = 
        \sum_{ \sigma \in \Sigma(k,n) } 
        w'_{\sigma} \, 
        \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}
        \in
        W^{2}\Lambda^{k-1}(\Omega)
    \end{gather}
    that satisfies $\cartan w' = \cartan u$ and $\trace_{\hat T,\hat\Gamma} w' = 0$. By construction, 
    \begin{align*}
        \| w' \|_{L^{2}(\hat T)}
        \leq 
        \| w \|_{L^{2}(\hat T)}
        \leq 
        2^{-\frac 1 2}
        \| \nabla w \|_{L^{2}(\hat T)}
        \leq 
        2^{-\frac 1 2}
        C_{??} % TODO
        \| \cartan u \|_{L^{2}(\hat T)}
        .
    \end{align*}

    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\Delta^n)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\widetilde \Makoto)}
        \leq 
        2^{\frac {n-\ell} p}
        \| \hat g \|_{L^{p}(\Delta^n)}
        &\leq 
        2^{\frac {n-\ell} p}
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
\end{proof}
